\documentclass[a4paper,10pt,notitlepage]{article}
\oddsidemargin -0.35in
\topmargin -0.8in
\textwidth 7in
\textheight 10in
\pagenumbering{gobble}
\usepackage[latin1]{inputenc}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{hyperref}
\usepackage[american]{babel}
\usepackage[dvips]{graphicx}
\usepackage{multicol}
%\renewcommand{\baselinestretch}{3}
\oddsidemargin 0.0in
%%this makes the odd side margin go to the default of 1inch
\textwidth 6.5in
\usepackage{fancyhdr}
\pagestyle{fancy}
\rhead{\large\bfseries Bryan Bischof}
\lhead{\large\bfseries R\'{e}sum\'{e}}
\begin{document}
\begin{multicols}{2}{
\noindent
1135 Page St. Apt. A\\
Berkeley, CA 94702

\noindent Phone: 412-953-7407\\
Personal Email: bryan.bischof@gmail.com\\
% Employer Email: bbischof@asperasoft.com
Homepage: \url{http://www.bbischof.com}
}
\end{multicols}

% \vspace{-10pt}\section*{Statement of Purpose}
\noindent \textit{\textbf{I am a mathematician-turned-data engineer with a penchant for applying rigorous quantitative thinking to difficult problems in the technology space. I am notorious for asking the right questions. I have a deep love for information presentation and communication. }}


\vspace{-10pt}\section*{Education}
\begin{itemize}
  % \vspace{-5pt}\item  Jun-Jul 2016: Stamen Design Building Interactive Maps with D3 Workshop
  \vspace{-5pt}\item  (Oct 2015-Jan 2016): Galvanize Data Engineering Immersive
  % \vspace{-5pt}\item  May 2015: Galvanize D3 Workshop
  \vspace{-5pt}\item  (Sept 2008-May 2014): Ph.D. in Mathematics, Kansas State University
    \begin{itemize}
     \vspace{-5pt}\item \textit{University Academic Excellence Award.}
     \vspace{-5pt}\item \textit{Surowski Memorial Fellowship Research Excellence Award.}
     \end{itemize}
  % \vspace{-5pt}\item  Sept 2004-May 2008: Bachelors Degree in Mathematics, Westminster College.
\end{itemize}

\vspace{-10pt}\section*{Professional Experience}

\subsubsection*{Blue Bottle Coffee (August 2016-Present): \textit{Senior Software Engineer}, Data Engineering and Machine Learning}
  \begin{itemize}
    \vspace{-5pt}\item  \textit{Demand Forecasting Engine} Daily predictions for 1000's of sku's $>50$ locations
    \vspace{-5pt}\item  \textit{Production Model and Prediction Deployments} Designed AWS architecture and deployment
    \vspace{-5pt}\item  \textit{Forecasting Pipeline and API} Job queue and messeging based pipeline
    \vspace{-5pt}\item  \textit{Data Warehouse Development} implemented micro-service DB's; designed DB views
    \vspace{-5pt}\item  \textit{BI Dashboarding, Performance Analysis} developed performance metrics, and build user dashboards
    \vspace{-5pt}\item  \textit{Project Planning and Development} greenfield project development, prototyped, and productize V1
    \vspace{-5pt}\item  \textit{Team Leadership} led two engineers in refactoring, and feature development
    \vspace{-5pt}\item  \textit{Deployment and DevOps} assisted in cloud infrastructure and devops for AWS ECS cluster
    \vspace{-5pt}\item  \textit{Testing and Containerization} Dockerized ML pipeline, integrated testing framework/jenkins (unit and integration)
    \vspace{-5pt}\item  \textit{Recommendation Engine} build a user-facing recommendation engine for coffee flavors
    \vspace{-5pt}\item  \textbf{Used Python, Ruby/Rails, StateSpace, Experimental Design, SQS, Redshift, SNS, ECS, pytest, Docker, Jenkins}
  \end{itemize}

\subsubsection*{Quasicoherent Labs (January 2016-Present): \textit{Founder}, Data Scientist}
  \begin{itemize}
    \vspace{-5pt}\item  \textit{MedForm Entry Efficiency Analysis} Experimental Design
    \vspace{-5pt}\item \textit{Recruit Forcasting} Throughput forecasting Kaggle competition (top30\% rank)
    \vspace{-5pt}\item \textit{When It Finally Happens} Research and Data Visualization Book Project
  \end{itemize}

\subsubsection*{IBM(Aspera Labs) (February 2014-July 2016): \textit{Software Engineer}, Research and Development}
  \begin{itemize}
  \vspace{-5pt}\item  \textit{Terabyte-scale Spark Streaming data pipeline for Timeseries analysis}
  \vspace{-5pt}\item  \textit{Data Visualization Dashboard and Log File Processing}
  \vspace{-5pt}\item  \textit{Livestream data transfer experimentation, analysis, and paper writing}
  \vspace{-5pt}\item  \textit{Research and prototyped a number of data products for integration with Aspera's core software. This ranges from researching ML algorithms in specialized fields, to extensive mathematical modeling of signals.}
  \vspace{-5pt}\item  \textit{Satellite network analysis}
  \vspace{-5pt}\item   \textbf{Used Scala, Spark, Kafka, Mesos, Python, REST API, JSON, Javascript, D3.js, CSS, HTML, Awk, Sed, BASH, GNUplot, C++, C, Ruby, jQuery, signal processing, statistics, control theory, experimental design.}
  \end{itemize}

\subsubsection*{Galvanize Data Engineering Immersive (October 2015-January 2016)}
  \begin{itemize}
    \vspace{-5pt} \item Project driven course covering several of the most popular and essential big data technologies, architectures, and algoritms. Solo and pair programming labs daily--implementing, problem solving, and testing.
    \vspace{-5pt} \item \textbf{Data Engineering Capstone}: Spark Streaming log file parser.
    \vspace{-5pt}\item  \textbf{Used Spark, Scala, Kafka, MapReduce, Hive, Pig, Sqoop, Flume, Scalding, HDFS, Hadoop, Python, REST API, JSON, Java, JUnit, and more}
  \end{itemize}


\end{document}
